03 - Analyses coding

### 2022-07-17 scripts/r/03_analyses_coding.Rmd
♻️ - join intake, reviews and models

@@

```{r load-models}
msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(
    path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))
  ) %>% 
  separate(
    mod_name, 
    into = c("word1", "word2", "model_n", "model_outcome", "typicality"), 
    sep = "_", remove = F,
    convert = TRUE
  ) %>% 
  unite(animal, word1, word2, sep = "_") %>% 
  select(animal, model_n:model) %>% 
  mutate(summaries = map(model, clean_up)) %>%
  select(-model) %>%
  unnest(summaries) %>%
  mutate(
    typ_level = case_when(
      term == "effect_cattypical" ~ "typical",
      term == "effect_catmedium" ~ "medium"
    ),
    typicality = ifelse(typicality == "con", "continuous", "categorical"),
    model_id = paste(animal, model_n, sep = "_")
  ) %>%
  select(animal, model_n, model_id, model_outcome, outcome_mult, typicality, typ_level, estimate, se) %>%
  mutate(
    outcome_mult = case_when(
      outcome_mult == "none" ~ NA_character_,
      outcome_mult == "meanf0" ~ "f0",
      outcome_mult == "meanint" ~ "intensity",
      outcome_mult == "duration" ~ "duration",
      outcome_mult == "f0" ~ "f0",
      outcome_mult == "f15" ~ "formants_1",
      outcome_mult == "f25" ~ "formants_2"
    )
  ) %>%
  left_join(y = coding) %>%
  mutate(
    model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_")),
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "other")),
    typicality = factor(typicality, levels = c("categorical", "continuous")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  )

>>>>

# Read intake forms

We will join the intake forms with `msa_models`.

```{r intake}
other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"

team_animal_coord <- read_sheet(other_sheet)

msa_intake <- read_csv("./data/questionnaires/msa_intake_form.csv") %>%
  filter(row_number() != 2)
msa_intake_qs <- msa_intake[1,]
msa_intake <- msa_intake[-1,]

msa_intake <- msa_intake %>%
  mutate(
    Q6 = case_when(
      Q6 == "Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
      Q6 == "University of Birmingham team under the team coordinator Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
      Q6 == "Vincent Hughes" ~ "Vince Hughes",
      Q6 == "Tiphaine Cordelier" ~ "Tiphaine Caudrelier",
      Q6 == "Scott Perry" ~ "Scott James Perry",
      Q6 == "Scott James Perru" ~ "Scott James Perry",
      Q6 == "Nicole Rodriquez" ~ "Nicole Rodriguez",
      Q6 == "Michael Gradoville (Arizona State Univ.)" ~ "Michael Gradoville",
      Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
      Q6 == "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)" ~ "Dušan Nikolić",
      Q6 == "Dusan Nikolic" ~ "Dušan Nikolić",
      Q6 == "Dušan Nickolić" ~ "Dušan Nikolić",
      Q6 == "Alicea Megan Brown" ~ "Alicia M Brown",
      Q6 == "Alicia Brown" ~ "Alicia M Brown",
      Q6 == "Ali A-Hoorie" ~ "Ali H. Al-Hoorie",
      Q6 == "Ali Al-Hoorie" ~ "Ali H. Al-Hoorie",
      Q6 == "Dr Rory Turnbull" ~ "Rory Turnbull",
      Q6 == "Dr. Reenu Punnoose" ~ "Reenu Punnoose",
      TRUE ~ Q6
    ),
    Q5 = as.numeric(Q5),
    Q7_1 = as.numeric(Q7_1)
  )

msa_intake_teams <- msa_intake %>%
  group_by(Q6) %>%
  summarise(
    years_from_phd = mean(Q5, na.rm = TRUE),
    years_from_phd_sd = sd(Q5, na.rm = TRUE),
    prior_belief = mean(Q7_1, na.rm = TRUE),
    prior_belief_sd = sd(Q7_1, na.rm = TRUE)
  ) %>%
  full_join(y = team_animal_coord, by = c("Q6" = "coordinator")) %>%
  select(-Q6)
```

# Read reviews

```{r}
msa_reviews <- readRDS("./data/peer_review/msa_reviews.rds")

msa_reviews_teams <- msa_reviews %>%
  group_by(Q3) %>%
  summarise(
    phon_rating = mean(Q5_2, na.rm = TRUE),
    phon_sd = sd(Q5_2, na.rm = TRUE),
    stat_rating = mean(Q5_3, na.rm = TRUE),
    stat_sd = sd(Q5_3, na.rm = TRUE),
    all_rating = mean(Q5_4, na.rm = TRUE),
    all_sd = sd(Q5_4, na.rm = TRUE),
  )
```

@@

```{r load-models}
msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(
    path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))
  ) %>% 
  separate(
    mod_name, 
    into = c("word1", "word2", "model_n", "model_outcome", "typicality"), 
    sep = "_", remove = F,
    convert = TRUE
  ) %>% 
  unite(animal, word1, word2, sep = "_") %>% 
  select(animal, model_n:model) %>% 
  mutate(summaries = map(model, clean_up)) %>%
  select(-model) %>%
  unnest(summaries) %>%
  mutate(
    typ_level = case_when(
      term == "effect_cattypical" ~ "typical",
      term == "effect_catmedium" ~ "medium"
    ),
    typicality = ifelse(typicality == "con", "continuous", "categorical"),
    model_id = paste(animal, model_n, sep = "_")
  ) %>%
  select(animal, model_n, model_id, model_outcome, outcome_mult, typicality, typ_level, estimate, se) %>%
  mutate(
    outcome_mult = case_when(
      outcome_mult == "none" ~ NA_character_,
      outcome_mult == "meanf0" ~ "f0",
      outcome_mult == "meanint" ~ "intensity",
      outcome_mult == "duration" ~ "duration",
      outcome_mult == "f0" ~ "f0",
      outcome_mult == "f15" ~ "formants_1",
      outcome_mult == "f25" ~ "formants_2"
    )
  ) %>%
  left_join(y = coding) %>%
  mutate(
    model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_")),
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "other")),
    typicality = factor(typicality, levels = c("categorical", "continuous")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  ) %>%
  left_join(y = msa_intake_teams) %>%
  left_join(y = msa_reviews_teams, by = c("animal" = "Q3"))
